Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
minor edits to abstract

\textbf{Abstract---}
We develop \sysname, a system to generate provably-correct configurations for large, evolving networks from high-level specifications of their topology, routing policy, and fault-tolerance requirements. It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance. Our analysis operates entirely on abstract topologies and guarantees correctness for all concrete instantiations of the topology. Its output is also guaranteed to require minimal changes to the configurations of existing devices when the topology evolves to include new devices or links. Our experiments with many real-world topologies and policies show that our abstractions and fault-tolerance analysis are effective and that, for large networks, configuration synthesis with \sysname is two orders of magnitude faster than systems that operate over concrete topologies.

>>>>

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct configurations for large, evolving networks from high-level specifications of topology, routing policy, and fault-tolerance requirements. It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the impact of topology and routing policy on fault tolerance. Our algorithms operates entirely on abstract topologies and guarantees correctness for all its concrete instantiations. \sysname also guarantees that minimal changes to existing device configurations are required when the network evolves to add or remove devices and links. Our experiments with real-world topologies and policies show that our abstractions and algorithms are effective and that, for large networks, \sysname synthesizes configurations two orders of magnitude faster than systems that operate over concrete topologies.
